---
title: "Homework1"
author: Bin Yang
output: github_document
---

library used for this homework.

```{r, echo = FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df <- 
 tibble(
  samp = rnorm(10),
  samp_gt_0 =  samp > 0,
  char_vec =  c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in the data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))

```

I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2

**Load the data set.**

```{r}
data("penguins", package = "palmerpenguins")
```

**A short description of the penguins data set.**

There are `r ncol(penguins)` variables, and `r nrow(penguins)` observations in total in the data set. A breif summary of the data set is: `r dplyr::glimpse(penguins)`. The mean flipper length is `r mean(pull(penguins, !is.na(flipper_length_mm))` mm. 
